\chapter{多附录}

\section{多附录}
\begin{thebibliography}{4}  
	\bibitem{ref1}Nan Jiang, Viswanathan Swaminathan, and Sheng Wei. 2017. Power Evaluation of 360 VR Video Streaming on Head Mounted Display Devices. In Proceedings of the 27th Workshop on Network and Operating Systems Support for Digital Audio and Video. ACM, 55–60.
	\bibitem{ref2}Xing Liu, Qingyang Xiao, Vijay Gopalakrishnan, Bo Han, Feng Qian, Matteo Varvello:360° Innovations for Panoramic Video Streaming. HotNets 2017: 50-56
	\bibitem{ref3}J. Chen, B. Li and R. Srikant, Thompson-Sampling-Based Wireless Transmission for Panoramic Video Streaming, 2020 18th International Symposium on Modeling and Optimization in Mobile, Ad Hoc, and Wireless Networks (WiOPT), 2020, pp. 1-3.
	\bibitem{ref4}Philbin J, Chum O, Isard M, et al. Lost in quantization: Improving particular object retrieval in large scale image databases, Computer Vision and Pattern Recognition, 2008. CVPR 2008, IEEE Conference on, IEEE, 2008: 1-8.  
	\bibitem{ref5}Tang M ,  Wong V . Online Bitrate Selection for Viewport Adaptive 360-Degree Video Streaming[J].  2020.
	\bibitem{ref6}L. Xie, X. Zhang, and Z. Guo, “CLS: A cross-user learning based system for improving QoE in 360-degree video adaptive streaming,” in Proc. ACM Int’l Conf. on Multimedia (MM), Seoul, Republic of Korea, Oct. 2018.
	\bibitem{ref7}Harsh Gupta, Jiangong Chen, Bin Li, R. Srikant, Online Learning-Based Rate Selection for Wireless Panoramic Video Streaming.
	\bibitem{ref8}J. Chen, B. Li and R. Srikant, Thompson-Sampling-Based Wireless Transmission for Panoramic Video Streaming, 2020 18th International Symposium on Modeling and Optimization in Mobile, Ad Hoc, and Wireless Networks (WiOPT), 2020, pp. 1-3.
\end{thebibliography}

\endinput
